\newpage
\section{Extrema}

\begin{definition}
Let $f$ be a function on $[a, b]$. We say $f$ has a local minimum at $c \in [a, b]$ if for any $\delta > 0$ we have, for all $x$ such that $\lvert x - c \rvert < \delta$, $f(x) \geq f(c)$.
\end{definition}

\begin{definition}
Let $f$ be a function on $[a, b]$. We say $f$ has a local maximum at $c \in [a, b]$ if for any $\delta > 0$ we have, for all $x$ such that $\lvert x - c \rvert < \delta$, $f(x) \leq f(c)$.
\end{definition}

\begin{theorem}
If $f$ has a local minimum or maximum at $c \in [a, b]$ and if $f^{'}(c)$ exists, then $f^{'}(c) = 0$.
\end{theorem}

\begin{definition}
Let $f$ be a function on $[a, b]$. We say $f$ has an absolute minimum, say at $c \in [a, b]$, if $f(c) \leq f(x)$ for all $x \in [a, b]$.
\end{definition}

\begin{definition}
Let $f$ be a function on $[a, b]$. We say $f$ has an absolute maximum, say at $c \in [a, b]$, if $f(c) \geq f(x)$ for all $x \in [a, b]$.
\end{definition}

\begin{theorem}
If function $f$ is defined on a closed and bounded interval $[a, b]$, then the range of $f$ will also be closed and bounded. Meaning
\begin{align*}
    f \hspace{10pt} \text{continuous on} \hspace{10pt} [a, b] \hspace{20pt} \Longrightarrow \hspace{20pt} \text{Rng}(f) = [c, d]
\end{align*}
This necessarily implies that $\text{Rng}(f)$ will contain an absolute maximum and an absolute minimum.
\end{theorem}

\begin{exercise}
If $a$ and $b$ are both positive numbers, then find the maximum value $f$, given $f$ is defined as follows
\begin{align*}
    f(x) = x^{a}(1-x)^{b} \hspace{20pt} x \in [0, 1]
\end{align*}
\end{exercise}

\begin{exercise}
An object with weight $W$ is dragged along a horizontal plane by a force acting along a rope attached to the object. If the rope makes an angle $\theta$ with the plane, then the magnitude of the force is 
\begin{align*}
    F(\theta) = \dfrac{\mu W}{\mu \sin(\theta) + \cos(\theta)} \hspace{20pt} \theta \in \Big[0, \dfrac{\pi}{2}\Big] 
\end{align*}
where $\mu$ is a positive constant called the coefficient of friction. Show that $F$ has a minimum at $\theta = \arctan(\mu)$.
\end{exercise}

\newpage
\section{The Mean Value Theorem}



\newpage
\section{L'Hospital's Rule}

L'Hospital's Rule is an application of differentiation that handles indeterminate forms $\dfrac{0}{0}$ and $\dfrac{\infty}{\infty}$ and $\dfrac{\pm \infty}{\mp \infty}$.

\vspace{0.1in}
\begin{theorem}
Let $-\infty \leq a < b \leq \infty$ and let $f, g$ be differentiable on $(a, b)$, with $g(x) \neq 0$ for all $a < x < b$. Suppose 
\begin{align*}
    \lim_{x \longrightarrow a^{+}} f(x) = 0 = \lim_{x \longrightarrow a^{+}} g(x)
\end{align*}
If
\begin{align*}
    \lim_{x \longrightarrow a^{+}} \dfrac{f^{'}(x)}{g^{'}(x)} = L \in \mathbb{R} \cup \{-\infty, \infty\}
\end{align*}
then
\begin{align*}
    \lim_{x \longrightarrow a^{+}} \dfrac{f(x)}{g(x)} = L
\end{align*}
\label{L'Hospital_1}
\end{theorem}

\begin{note}
This theorem applies in the same way for left-sided and two-sided limits.
\end{note}

\begin{theorem}
Let $-\infty \leq a < b \leq \infty$ and let $f, g$ be differentiable on $(a, b)$, where $g(x) \neq 0$ for all $a < x < b$. Suppose
\begin{align*}
    \lim_{x \longrightarrow a^{+}} g(x) = \pm \infty 
\end{align*}
If
\begin{align*}
    \lim_{x \longrightarrow a^{+}} \dfrac{f^{'}(x)}{g^{'}(x)} = L \in \mathbb{R} \cup \{-\infty, \infty\}
\end{align*}
then
\begin{align*}
    \lim_{x \longrightarrow a^{+}} \dfrac{f(x)}{g(x)} = L
\end{align*}
\label{L'Hospital_2}
\end{theorem}

\begin{note}
This theorem applies in the same way for left-sided and two-sided limits.
\end{note}

\begin{note}
For Theorem \ref{L'Hospital_2}, we only require $\lim_{x \longrightarrow a^{+}} g(x) = \pm \infty$. If 
\begin{align*}
    \lim_{x \longrightarrow a^{+}} f(x)
\end{align*} 
is finite,
\begin{align*}
    \lim_{x \longrightarrow a^{+}} \dfrac{f(x)}{g(x)} = 0
\end{align*}
and L'Hospital's Rule is not required. So, L'Hospital's Rule is only used if both $f, g$ have infinite limits.
\end{note}

\begin{note}
Indeterminate forms, such as
\begin{align*}
    &\infty - \infty\\
    &0 \cdot \infty\\
    &1^{\infty}\\
    &0^{0}\\
    &\infty^{0}
\end{align*}
can be reduced to those cases considered previously in Theorem \ref{L'Hospital_1} and Theorem \ref{L'Hospital_2}.
\end{note}